Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-04-29 concurrency/CONCUR 2023/paper.tex
fixed proof mechanization part

%By utilizing VST, we can create programs in standard C, automatically generate abstract syntax trees (ASTs) for them in Coq, and subsequently state and interactively prove specifications for these programs with the support of automated tactics. Table \ref{table_coq} presents a summary of our Coq development. We formalized all previously described proofs in Coq, taking advantage of VST's features for verifying separation logic specifications of C functions. This encompasses supplementary proofs, template specifications (encompassing all helper functions such as \texttt{findNext}, \texttt{insertOp}, and others, in addition to \texttt{traverse}, \texttt{insert}, \texttt{lookup}, and \texttt{delete}), as well as proofs against with lock-coupling and give-up template specifications. 
%\wm{Rather than re-stating what we proved, this is the place to discuss the development: e.g., which parts took the most effort and LoC, which parts we expect to be reusable and in what way, how much bigger or smaller the template proofs were than non-template versions, etc.}
The construction of proofs for the \texttt{traverse} function, in the contexts of both lock-coupling and give-up templates, demanded substantial effort and lines of code (LoC). However, we expect that functions such as \texttt{traverse}, \texttt{inRange}, \texttt{insert}, and \texttt{lookup} will be reusable with only minor adjustments needed.  The methods \texttt{findNext} and \texttt{insertOp} may also be adapted to other data structures, such as linked lists, with some additional effort. 
Specifically, when attempting to prove concurrent linked lists, we plan to tweak the specifications of \texttt{findNext} and \texttt{insertOp} to restructure the \texttt{node} struct. While the size of our template proofs currently approximates that of the no-template versions, we anticipate that strategic application of simple tactics for quantifier expansion could significantly streamline these proofs in the future. The full development of our mechanization effort is available online
\href{https://github.com/PrincetonUniversity/DeepSpecDB/tree/master/concurrency/templates}{\color{blue}{https://github.com/PrincetonUniversity/DeepSpecDB/tree/master/concurrency/templates}}.

>>>>

%By utilizing VST, we can create programs in standard C, automatically generate abstract syntax trees (ASTs) for them in Coq, and subsequently state and interactively prove specifications for these programs with the support of automated tactics. Table \ref{table_coq} presents a summary of our Coq development. We formalized all previously described proofs in Coq, taking advantage of VST's features for verifying separation logic specifications of C functions. This encompasses supplementary proofs, template specifications (encompassing all helper functions such as \texttt{findNext}, \texttt{insertOp}, and others, in addition to \texttt{traverse}, \texttt{insert}, \texttt{lookup}, and \texttt{delete}), as well as proofs against with lock-coupling and give-up template specifications. 
%\wm{Rather than re-stating what we proved, this is the place to discuss the development: e.g., which parts took the most effort and LoC, which parts we expect to be reusable and in what way, how much bigger or smaller the template proofs were than non-template versions, etc.}

Even though the proof for the \texttt{insert} function within the lock-coupling templates was line-of-code (LoC) intensive, future enhancements could significantly streamline this process. Otherwise, the construction of proofs for the \texttt{traverse} function, in the contexts of both lock-coupling and give-up templates, necessitated a considerable amount of time and effort.
However, we expect that functions such as \texttt{traverse}, \texttt{inRange}, \texttt{insert}, and \texttt{lookup} will be reusable with only minor adjustments needed.  The methods \texttt{findNext} and \texttt{insertOp} may also be adapted to other data structures, such as linked lists, with some additional effort. 
Specifically, when attempting to prove concurrent linked lists, we plan to tweak the specifications of \texttt{findNext} and \texttt{insertOp} to restructure the \texttt{node} struct. While the size of our template proofs currently approximates that of the no-template versions, we anticipate that strategic application of simple tactics for quantifier expansion could significantly streamline these proofs in the future. The full development of our mechanization effort is available online
\href{https://github.com/PrincetonUniversity/DeepSpecDB/tree/master/concurrency/templates}{\color{blue}{https://github.com/PrincetonUniversity/DeepSpecDB/tree/master/concurrency/templates}}.
